Austria's Covid legislation: Duration of parliamentarian consultation period in comparision.

### 2021-02-23 _post/2020-02-07-bih-voting-behavior-of-mps-in-house-of-representatives/bih-voting-behavior-of-mps-in-house-of-representatives.Rmd
subtitles added

---
title: "Bosnia: Voting behavior of MPs in the House of Representatives"
description: |
  A short description of the post.
date: 02-07-2020

>>>>

---
title: "Bosnia: Voting behavior of MPs in the House of Representatives"
description: |
  Creating and analysing a new dataset on the voting behavior of BiH's members of the House of Representatives.
date: 02-07-2020

### 2021-02-23 _post/2020-07-21-attransperency/attransperency.Rmd
subtitles added

---
title: "Austrian Parliament: MPs transparency and conflict of interest report"
description: |
  A short description of the post.

@@

# preview: austrian-parliament-mps-transparency-and-conflict-of-interest-report_files/preview.png

>>>>

---
title: "Austrian Parliament: MPs transparency and conflict of interest report"
description: |
  Analysis of Austria MP's transparency reports.

@@

preview: attransperency_files/preview.png #speeling errors

### 2021-02-23 _post/2021-01-22-covidconsultationduration/covidconsultationduration.Rmd
subtitles added

pl_length_duration <- df_consolidated %>% 
  filter(duration_collected<21) %>% 
  filter(duration_collected>-1) %>% 
  filter(pdf_pages_sum<11) %>% 
  mutate(pdf_pages_sum_fct=forcats::fct_inseq(as.character(pdf_pages_sum))) %>% 
  mutate(duration_collected_fct=fct_inseq(as.character(duration_collected)) %>% fct_rev()) %>% 
  ggplot()+
  labs(title="Duration of consultation process and length of considered bills:",
       subtitle = "",
       caption=glue::glue("{str_wrap(caption_note, 125)}

>>>>

pl_length_duration <- df_consolidated %>% 
  filter(duration_collected<21) %>% 
  filter(duration_collected>0) %>% 
  filter(pdf_pages_sum<11) %>% 
  mutate(pdf_pages_sum_fct=forcats::fct_inseq(as.character(pdf_pages_sum))) %>% 
  mutate(duration_collected_fct=fct_inseq(as.character(duration_collected)) %>% fct_rev()) %>% 
  ggplot()+
  labs(title="Duration of consultation process and length of considered bills:",
       subtitle = "",
       caption=glue::glue("{str_wrap(caption_note, 125)}
